---
title: "The effects of variability and similarity on talker-independent adaptation to Spanish-accented English: Full model outputs"
author: Holly A. Zaharchuk and Janet G. van Hell
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

# Set up session

```{r setup_2}
# Source packages, datasets, etc.
source("/Users/hollyzaharchuk/Mirror/dissertation/16_jml/sections/code/0_load_behave.R")
```

# Experiment 1: Investigating differences in generalization from exposure to Spanish-accented stops versus fricatives

## Exposure: Accuracy

### Filter, factor, and scale variables

```{r exp_1_1}
# Filter and factor
dat_exp_1 <- dat_exp_filt %>%
  dplyr::filter(version == "1a") %>%
  mutate(across(.cols = c("participant", "stim", "type",
                          "cond_sim", "cond_var"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_cent = scale(FreqZipfUS)[,1])

# Add contrasts
contrasts(dat_exp_1$cond_sim) <- contrast_sim_1a
contrasts(dat_exp_1$cond_var) <- contrast_var
contrasts(dat_exp_1$type) <- contrast_type
```

### Run model

```{r exp_1_2, cache = TRUE}
# Run
exp_acc_1 <- glmer(resp_acc ~ cond_var*cond_sim*type +
                      trial_cent + freq_cent + vot_cent +
                      (1|stim) + (1|participant),
                    data = dat_exp_1,
                    family = binomial,
                    control = glmerControl(optimizer = "bobyqa"))

# Show
summary(exp_acc_1)
```

### Test effects

```{r exp_1_3}
# Test effects
exp_acc_1_comp <- Anova(exp_acc_1, test = "Chi", type = "III")

# Show
exp_acc_1_comp
```

### Get means: Variability x Similarity x Word type interaction

```{r exp_1_4}
# Get means
exp_acc_1_means <- emmeans(exp_acc_1, ~ cond_var*cond_sim*type)

# Show
exp_acc_1_means %>% summary(type = "response")
```

### Compare means: Variability x Similarity x Word type interaction

```{r exp_1_5}
# Contrasts by Variability
exp_acc_1_cont_var <- pairs(exp_acc_1_means, 
                             by = c("type", "cond_var"), 
                             adj = "hommel")

# Show
exp_acc_1_cont_var

# Contrasts by Similarity
exp_acc_1_cont_sim <- pairs(exp_acc_1_means, 
                             by = c("type", "cond_sim"), 
                             adj = "hommel")

# Show
exp_acc_1_cont_sim
```

## Exposure: RT

### Filter, factor, and scale variables

```{r exp_1_6}
# Filter and factor
dat_exp_1_rt <- dat_exp_rt %>%
  dplyr::filter(version == "1a") %>%
  left_join(tab_factor_1a, by = c("cond_var", "cond_sim")) %>%
  left_join(tab_type, by = c("type")) %>%
  mutate(across(.cols = c("participant", "stim", "type",
                          "cond_sim", "cond_var"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_cent = scale(FreqZipfUS)[,1]) 

# Add contrasts
contrasts(dat_exp_1_rt$cond_sim) <- contrast_sim_1a
contrasts(dat_exp_1_rt$cond_var) <- contrast_var
contrasts(dat_exp_1_rt$type) <- contrast_type
```

### Run model

```{r exp_1_7, cache = TRUE}
# Run
exp_rt_1 <- lmer(inv_rt ~ cond_var*cond_sim*type + 
                    trial_cent + freq_cent + vot_cent +
                    (1|stim) + (1|participant),
                  data = dat_exp_1_rt)

# Show
summary(exp_rt_1)
```

### Test effects

```{r exp_1_8}
# Test effects
exp_rt_1_comp <- Anova(exp_rt_1, test = "Chi", type = "III")

# Show
exp_rt_1_comp
```

### Get means: Variability x Similarity x Word type interaction

```{r exp_1_9}
# Means
exp_rt_1_means <- emmeans(exp_rt_1, ~ cond_var*cond_sim*type)

# Show
exp_rt_1_means %>% apa_rt() %>% select(-report)
```

### Compare means: Variability x Similarity x Word type interaction

```{r exp_1_10}
# Contrasts by Variability
exp_rt_1_cont_var <- pairs(exp_rt_1_means, 
                             by = c("type", "cond_var"), 
                             adj = "hommel")

# Show
exp_rt_1_cont_var

# Contrasts by Similarity
exp_rt_1_cont_sim <- pairs(exp_rt_1_means, 
                             by = c("type", "cond_sim"), 
                             adj = "hommel")

# Show
exp_rt_1_cont_sim
```

## Test 1: Accuracy

### Filter, factor, and scale variables

```{r test_1_1}
# Filter and factor
dat_test_1 <- dat_test_filt %>%
  dplyr::filter(version %in% c("1a", "1c")) %>%
  mutate(across(.cols = c("participant", "prime", "target", "match_type"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_prime_cent = scale(FreqZipfUS_prime)[,1],
         freq_target_cent = scale(FreqZipfUS_target)[,1]) %>%
  left_join(tab_exp_1a, by = "cond_exp")

# Add contrasts
contrasts(dat_test_1$cond_exp_fac) <- contrast_train_1a
contrasts(dat_test_1$match_type) <- contrast_match_1
```

### Run model

```{r test_1_2, cache = TRUE}
# Run
test_acc_1_train <- glmer(resp_acc ~ cond_exp_fac*match_type + 
                             trial_cent + freq_prime_cent:freq_target_cent + 
                             vot_cent +
                             (1|prime:target) + (1|participant),
                           data = dat_test_1,
                           family = binomial,
                           control = glmerControl(optimizer = "bobyqa"))

# Show
summary(test_acc_1_train)
```

### Test effects

```{r test_1_3}
# Test effects
test_acc_1_train_comp <- Anova(test_acc_1_train, test = "Chi", type = "III")

# Show
test_acc_1_train_comp
```

### Get means: Main effect of Exposure

```{r test_1_4}
# Across levels of Target
test_acc_1_train_means_simple <- emmeans(test_acc_1_train, ~ cond_exp_fac)

# Show
test_acc_1_train_means_simple %>% summary(type = "response")
```

### Compare means: Main effect of Exposure

```{r test_1_5}
# Select contrasts with Test-only group
test_acc_1_train_coef_simple <-
  emmeans:::pairwise.emmc(levels(test_acc_1_train_means_simple)$cond_exp_fac)
test_acc_1_train_coef_simple <- test_acc_1_train_coef_simple[c(1:6)]

# Run contrasts
test_acc_1_train_cont_simple <- contrast(test_acc_1_train_means_simple,
                                          test_acc_1_train_coef_simple, 
                                          adj = "hommel")

# Show
summary(test_acc_1_train_cont_simple)
```

### Get means: Exposure x Target type interaction

```{r test_1_6}
# By levels of Target
test_acc_1_train_means <- emmeans(test_acc_1_train, ~ cond_exp_fac*match_type)

# Show
test_acc_1_train_means %>% summary(type = "response")
```

### Compare means: Exposure x Target type interaction

```{r test_1_7}
# Select contrasts with Test-only group
test_acc_1_train_coef <- emmeans:::pairwise.emmc(levels(test_acc_1_train_means)$cond_exp_fac)
test_acc_1_train_coef_1 <- test_acc_1_train_coef[c(1:6)]


# Run contrasts
test_acc_1_train_cont_1 <- contrast(test_acc_1_train_means, 
                                   test_acc_1_train_coef_1, 
                                   by = "match_type",
                                   adj = "hommel")

# Show
test_acc_1_train_cont_1

# Select contrasts without Test-only group
test_acc_1_train_coef_2 <- test_acc_1_train_coef[c(7:21)]

# Run contrasts
test_acc_1_train_cont_2 <- contrast(test_acc_1_train_means, 
                                   test_acc_1_train_coef_2, 
                                   by = "match_type",
                                   adj = "hommel")

# Show
test_acc_1_train_cont_2
```

## Test 1: RT

### Filter, factor, and scale variables

```{r test_1_8}
# Filter and factor
dat_test_1_rt <- dat_test_rt %>%
  dplyr::filter(version %in% c("1a", "1c")) %>%
  mutate(across(.cols = c("participant", "prime", "target", "match_type"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_prime_cent = scale(FreqZipfUS_prime)[,1],
         freq_target_cent = scale(FreqZipfUS_target)[,1]) %>%
  left_join(tab_exp_1a, by = "cond_exp")

# Add contrasts
contrasts(dat_test_1_rt$cond_exp_fac) <- contrast_train_1a
contrasts(dat_test_1_rt$match_type) <- contrast_match_1
```

### Run model

```{r test_1_9, cache = TRUE}
# Run
test_rt_1_train <- lmer(inv_rt ~ cond_exp_fac*match_type + 
                           trial_cent + freq_prime_cent:freq_target_cent + 
                           vot_cent +
                           (1|prime:target) + (1|participant),
                         data = dat_test_1_rt)

# Show
summary(test_rt_1_train)
```

### Test effects

```{r test_1_10}
# Test effects
test_rt_1_train_comp <- Anova(test_rt_1_train, test = "Chi", type = "III")

# Show
test_rt_1_train_comp
```

### Get means: Exposure x Target type interaction

```{r test_1_11}
# Get means
test_rt_1_train_means <- emmeans(test_rt_1_train, ~ cond_exp_fac*match_type)

# Show
test_rt_1_train_means %>% apa_rt() %>% select(-report)
```

### Compare means: Exposure x Target type interaction

```{r test_1_12}
# Select contrasts with Test-only group
test_rt_1_train_coef <- emmeans:::pairwise.emmc(levels(test_rt_1_train_means)$cond_exp_fac)
test_rt_1_train_coef_1 <- test_rt_1_train_coef[c(1:6)]

# Run contrasts
test_rt_1_train_cont_1 <- contrast(test_rt_1_train_means, 
                                   test_rt_1_train_coef_1, 
                                   by = "match_type",
                                   adj = "hommel")

# Show
test_rt_1_train_cont_1

# Select contrasts wtihout Test-only group
test_rt_1_train_coef_2 <- test_rt_1_train_coef[c(7:21)]

# Run contrasts
test_rt_1_train_cont_2 <- contrast(test_rt_1_train_means, 
                                   test_rt_1_train_coef_2, 
                                   by = "match_type",
                                   adj = "hommel")

# Show
test_rt_1_train_cont_2
```

# Experiment 2: Investigating the specificity of generalization from exposure to Spanish-accented stops

## Exposure: Accuracy

### Filter, factor, and scale variables

```{r exp_2_1}
# Filter and factor
dat_exp_2 <- dat_exp_filt %>%
  dplyr::filter(version == "1b") %>%
  mutate(across(.cols = c("participant", "stim", "type",
                          "cond_sim", "cond_var"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_cent = scale(FreqZipfUS)[,1])

# Add contrasts
contrasts(dat_exp_2$cond_sim) <- contrast_sim
contrasts(dat_exp_2$cond_var) <- contrast_var
contrasts(dat_exp_2$type) <- contrast_type
```

### Run model

```{r exp_2_2, cache = TRUE}
# Run
exp_acc_2 <- glmer(resp_acc ~ cond_var*cond_sim*type + 
                      trial_cent + freq_cent + vot_cent +
                      (1|stim) + (cond_var*cond_sim|participant),
                    data = dat_exp_2,
                    family = binomial,
                    control = glmerControl(optimizer = "bobyqa"))

# Show
summary(exp_acc_2)
```

### Test effects

```{r exp_2_3}
# Test effects
exp_acc_2_comp <- Anova(exp_acc_2, test = "Chi", type = "III")

# Show
exp_acc_2_comp
```

### Get means: Variability x Similarity x Word type interaction

```{r exp_2_4}
# Get means
exp_acc_2_means <- emmeans(exp_acc_2, ~ cond_var*cond_sim*type)

# Show
exp_acc_2_means %>% summary(type = "response")
```

### Compare means: Variability x Similarity x Word type interaction

```{r exp_2_5}
# Contrasts by Variability
exp_acc_2_cont_var <- pairs(exp_acc_2_means, 
                             by = c("type", "cond_var"), 
                             adj = "hommel")

# Show
exp_acc_2_cont_var

# Contrasts by Similarity
exp_acc_2_cont_sim <- pairs(exp_acc_2_means, 
                             by = c("type", "cond_sim"), 
                             adj = "hommel")

# Show
exp_acc_2_cont_sim
```

## Exposure: RT

### Filter, factor, and scale variables

```{r exp_2_6}
# Filter and factor
dat_exp_2_rt <- dat_exp_rt %>%
  dplyr::filter(version == "1b") %>%
  left_join(tab_factor, by = c("cond_var", "cond_sim")) %>%
  left_join(tab_type, by = c("type")) %>%
  mutate(across(.cols = c("participant", "stim", "type",
                          "cond_sim", "cond_var"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_cent = scale(FreqZipfUS)[,1])

# Add contrasts
contrasts(dat_exp_2_rt$cond_sim) <- contrast_sim
contrasts(dat_exp_2_rt$cond_var) <- contrast_var
contrasts(dat_exp_2_rt$type) <- contrast_type
```

### Run model

```{r exp_2_7, cache = TRUE}
# Run
exp_rt_2 <- lmer(inv_rt ~ cond_var*cond_sim*type + 
                    trial_cent + freq_cent + vot_cent +
                    (1|stim) + (1|participant),
                  data = dat_exp_2_rt)

# Show
summary(exp_rt_2)
```

### Test effects

```{r exp_2_8}
# Test effects
exp_rt_2_comp <- Anova(exp_rt_2, test = "Chi", type = "III")

# Show
exp_rt_2_comp
```

### Get means: Variabilty x Word type interaction

```{r exp_2_9}
# Means
exp_rt_2_means_2 <- emmeans(exp_rt_2, ~ cond_var*type)

# Show
exp_rt_2_means_2 %>% apa_rt() %>% select(-report)
```

### Compare means: Variabilty x Word type interaction

```{r exp_2_10}
# Contrasts by Variability
exp_rt_2_cont_2 <- pairs(exp_rt_2_means_2, 
                             by = "type", 
                             adj = "hommel")

# Show
exp_rt_2_cont_2
```

### Get means: Variability x Similarity x Word type interaction

```{r exp_2_11}
# Means
exp_rt_2_means_3 <- emmeans(exp_rt_2, ~ cond_var*cond_sim*type)

# Show
exp_rt_2_means_3 %>% apa_rt() %>% select(-report)
```

### Compare means: Variability x Similarity x Word type interaction

```{r exp_2_12}
# Contrasts by Variability
exp_rt_2_cont_var <- pairs(exp_rt_2_means_3, 
                             by = c("type", "cond_var"), 
                             adj = "hommel")

# Show
exp_rt_2_cont_var

# Contrasts by Similarity
exp_rt_2_cont_sim <- pairs(exp_rt_2_means_3, 
                             by = c("type", "cond_sim"), 
                             adj = "hommel")

# Show
exp_rt_2_cont_sim
```

## Test 1: Accuracy

### Filter, factor, and scale variables

```{r test_2_1}
# Filter and factor
dat_test_2 <- dat_test_filt %>%
  dplyr::filter(version %in% c("1b", "1c")) %>%
  mutate(across(.cols = c("participant", "prime", "target", "match_type"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_prime_cent = scale(FreqZipfUS_prime)[,1],
         freq_target_cent = scale(FreqZipfUS_target)[,1]) %>%
  left_join(tab_exp, by = "cond_exp")

# Add contrasts
contrasts(dat_test_2$cond_exp_fac) <- contrast_train
contrasts(dat_test_2$match_type) <- contrast_match_1
```

### Run model

```{r test_2_2, cache = TRUE}
# Run
test_acc_2_train <- glmer(resp_acc ~ cond_exp_fac*match_type + 
                       trial_cent + freq_prime_cent:freq_target_cent + 
                         vot_cent +
                       (1|prime:target) + (1|participant),
                     data = dat_test_2,
                     family = binomial,
                     control = glmerControl(optimizer = "bobyqa"))

# Show
summary(test_acc_2_train)
```

### Test effects

```{r test_2_3}
# Test effects
test_acc_2_train_comp <- Anova(test_acc_2_train, test = "Chi", type = "III")

# Format
test_acc_2_train_comp
```

### Get means: Exposure x Target type interaction

```{r test_2_4}
# Get means
test_acc_2_train_means <- emmeans(test_acc_2_train, ~ cond_exp_fac*match_type)

# Format
test_acc_2_train_means %>% summary(type = "response")
```

### Compare means: Exposure x Target type interaction

```{r test_2_5}
# Select contrasts for Test-only group
test_acc_2_train_coef <- emmeans:::pairwise.emmc(levels(test_acc_2_train_means)$cond_exp_fac)
test_acc_2_train_coef_1 <- test_acc_2_train_coef[c(1:4)]

# Run contrasts
test_acc_2_train_cont_1 <- contrast(test_acc_2_train_means, 
                                   test_acc_2_train_coef_1, 
                                   by = "match_type",
                                   adj = "hommel")

# Show
test_acc_2_train_cont_1

# Select contrasts without Test-only group
test_acc_2_train_coef_2 <- test_acc_2_train_coef[c(5:10)]

# Run contrasts
test_acc_2_train_cont_2 <- contrast(test_acc_2_train_means, 
                                   test_acc_2_train_coef_2, 
                                   by = "match_type",
                                   adj = "hommel")

# Show
test_acc_2_train_cont_2
```

## Test 1: RT

### Filter, factor, and scale variables

```{r test_2_6}
# Filter and factor
dat_test_2_rt <- dat_test_rt %>%
  dplyr::filter(version %in% c("1b", "1c")) %>%
  mutate(across(.cols = c("participant", "prime", "target", "match_type"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_prime_cent = scale(FreqZipfUS_prime)[,1],
         freq_target_cent = scale(FreqZipfUS_target)[,1]) %>%
  left_join(tab_exp, by = "cond_exp")

# Add contrasts
contrasts(dat_test_2_rt$cond_exp_fac) <- contrast_train
contrasts(dat_test_2_rt$match_type) <- contrast_match_1
```

### Run model

```{r test_2_7, cache = TRUE}
# Run
test_rt_2_train <- lmer(inv_rt ~ cond_exp_fac*match_type + 
                           trial_cent + freq_prime_cent:freq_target_cent + 
                           vot_cent +
                       (1|prime:target) + (1|participant),
                     data = dat_test_2_rt)

# Show
summary(test_rt_2_train)
```

### Test effects

```{r test_2_8}
# Test effects
test_rt_2_train_comp <- Anova(test_rt_2_train, test = "Chi", type = "III")

# Format
test_rt_2_train_comp
```

### Get means: Exposure x Target type interaction

```{r test_2_9}
# Get means
test_rt_2_train_means <- emmeans(test_rt_2_train, ~ cond_exp_fac*match_type)

# Show
test_rt_2_train_means %>% apa_rt() %>% select(-report)
```

### Compare means: Exposure x Target type interaction

```{r test_2_10}
# Select contrasts for Test-only group
test_rt_2_train_coef <- emmeans:::pairwise.emmc(levels(test_rt_2_train_means)$cond_exp_fac)
test_rt_2_train_coef_1 <- test_rt_2_train_coef[c(1:4)]

# Run contrasts
test_rt_2_train_cont_1 <- contrast(test_rt_2_train_means, 
                                   test_rt_2_train_coef_1, 
                                   by = "match_type",
                                   adj = "hommel")

# Show
test_rt_2_train_cont_1

# Select contrasts without Test-only group
test_rt_2_train_coef_2 <- test_rt_2_train_coef[c(5:10)]

test_rt_2_train_cont_2 <- contrast(test_rt_2_train_means, 
                                   test_rt_2_train_coef_2, 
                                   by = "match_type",
                                   adj = "hommel")

# Show
test_rt_2_train_cont_2
```

# Experiment 3: Investigating fine-grained perceptual changes from exposure to Spanish-accented stops

## Exposure: Accuracy

### Filter, factor, and scale variables

```{r exp_3_1}
# Filter and factor
dat_exp_3 <- dat_exp_filt %>%
  dplyr::filter(version == "2a") %>%
  mutate(across(.cols = c("participant", "stim", "type",
                          "cond_sim", "cond_var"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_cent = scale(FreqZipfUS)[,1])

# Add contrasts
contrasts(dat_exp_3$cond_sim) <- contrast_sim
contrasts(dat_exp_3$cond_var) <- contrast_var
contrasts(dat_exp_3$type) <- contrast_type
```

### Run model

```{r exp_3_2, cache = TRUE}
# Run
exp_acc_3 <- glmer(resp_acc ~ cond_var*cond_sim*type + 
                     trial_cent + freq_cent + vot_cent +
                     (1|stim) + (cond_var:cond_sim + cond_var|participant),
                   data = dat_exp_3,
                   family = binomial,
                   control = glmerControl(optimizer = "bobyqa"))

# Show
summary(exp_acc_3)
```

### Test effects

```{r exp_3_3}
# Test effects
exp_acc_3_comp <- Anova(exp_acc_3, test = "Chi", type = "III")

# Show
exp_acc_3_comp
```

### Get means: Variability x Word type interaction

```{r exp_3_4}
# Get means
exp_acc_3_means_2 <- emmeans(exp_acc_3, ~ cond_var*type)

# Show
exp_acc_3_means_2 %>% summary(type = "response")
```

### Compare means: Variability x Word type interaction

```{r exp_3_5}
# Run contrasts
exp_acc_3_cont_2 <- pairs(exp_acc_3_means_2, 
                          by = "type", 
                          adjust = "hommel")

# Show
exp_acc_3_cont_2
```

### Get means: Variability x Similarity x Word type interaction

```{r exp_3_6}
# Get means
exp_acc_3_means_3 <- emmeans(exp_acc_3, ~ cond_var*cond_sim*type)

# Show
exp_acc_3_means_3 %>% summary(type = "response")
```

### Compare means: Variability x Similarity x Word type interaction

```{r exp_3_7}
# Contrasts by Variability
exp_acc_3_cont_var <- pairs(exp_acc_3_means_3, 
                             by = c("type", "cond_var"), 
                             adj = "hommel")

# Show
exp_acc_3_cont_var

# Contrasts by Similarity
exp_acc_3_cont_sim <- pairs(exp_acc_3_means_3, 
                             by = c("type", "cond_sim"), 
                             adj = "hommel")

# Show
exp_acc_3_cont_sim
```

## Exposure: RT

### Filter, factor, and scale variables

```{r exp_3_8}
# Filter and factor
dat_exp_3_rt <- dat_exp_rt %>%
  dplyr::filter(version == "2a") %>%
  left_join(tab_factor, by = c("cond_var", "cond_sim")) %>%
  left_join(tab_type, by = c("type")) %>%
  mutate(across(.cols = c("participant", "stim", "type",
                          "cond_sim", "cond_var"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_cent = scale(FreqZipfUS)[,1])

# Add contrasts
contrasts(dat_exp_3_rt$cond_sim) <- contrast_sim
contrasts(dat_exp_3_rt$cond_var) <- contrast_var
contrasts(dat_exp_3_rt$type) <- contrast_type
```

### Run model

```{r exp_3_9, cache = TRUE}
# Run
exp_rt_3 <- lmer(inv_rt ~ cond_var*cond_sim*type + 
                   trial_cent + freq_cent + vot_cent +
                   (1|stim) + (1|participant),
                 data = dat_exp_3_rt)

# Show
summary(exp_rt_3)
```

### Test effects

```{r exp_3_10}
# Test effects
exp_rt_3_comp <- Anova(exp_rt_3, test = "Chi", type = "III")

# Show
exp_rt_3_comp
```

### Get means: Variability x Similarity x Word type interaction

```{r exp_3_11}
# Get means
exp_rt_3_means_3 <- emmeans(exp_rt_3, ~ cond_var*cond_sim*type)

# Show
exp_rt_3_means_3 %>% apa_rt() %>% select(-report)
```

### Compare means: Variability x Similarity x Word type interaction

```{r exp_3_12}
# Contrasts by Variability
exp_rt_3_cont_var <- pairs(exp_rt_3_means_3, 
                             by = c("type", "cond_var"), 
                             adj = "hommel")

# Show
exp_rt_3_cont_var

# Contrasts by Similarity
exp_rt_3_cont_sim <- pairs(exp_rt_3_means_3, 
                             by = c("type", "cond_sim"), 
                             adj = "hommel")

# Show
exp_rt_3_cont_sim
```

## Test 1: Accuracy

### Filter, factor, and scale variables

```{r test_3_1}
# Filter and factor
dat_test_3 <- dat_test_filt %>%
  dplyr::filter(version %in% c("2a", "2b")) %>%
  mutate(across(.cols = c("participant", "prime", "target", "match_type"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_prime_cent = scale(FreqZipfUS_prime)[,1],
         freq_target_cent = scale(FreqZipfUS_target)[,1]) %>%
  left_join(tab_exp, by = "cond_exp")

# Add contrasts
contrasts(dat_test_3$cond_exp_fac) <- contrast_train
contrasts(dat_test_3$match_type) <- contrast_match_2
```

### Run model

```{r test_3_2, cache = TRUE}
# Run
test_acc_3_train <- glmer(resp_acc ~ cond_exp_fac*match_type + 
                            trial_cent + freq_prime_cent:freq_target_cent + 
                            vot_cent +
                            (1|prime:target) + (1|participant),
                          data = dat_test_3,
                          family = binomial,
                          control = glmerControl(optimizer = "bobyqa"))

# Show
summary(test_acc_3_train)
```

### Test effects

```{r test_3_3}
# Test effects
test_acc_3_train_comp <- Anova(test_acc_3_train, test = "Chi", type = "III")

# Show
test_acc_3_train_comp
```

### Get means: Exposure x Target type interaction

```{r test_3_4}
# Get means
test_acc_3_train_means <- emmeans(test_acc_3_train, ~ cond_exp_fac*match_type)

# Show
test_acc_3_train_means %>% summary(type = "response")
```

### Compare means: Exposure x Target type interaction

```{r test_3_5}
# Select contrasts for Test-only group
test_acc_3_train_coef <- emmeans:::pairwise.emmc(levels(test_acc_3_train_means)$cond_exp_fac)
test_acc_3_train_coef_1 <- test_acc_3_train_coef[c(1:4)]

# Run contrasts
test_acc_3_train_cont_1 <- contrast(test_acc_3_train_means, 
                                  test_acc_3_train_coef_1, 
                                  by = "match_type", 
                                  adj = "hommel")

# Show
test_acc_3_train_cont_1

# Select contrasts without Test-only group
test_acc_3_train_coef_2 <- test_acc_3_train_coef[c(5:10)]

# Run contrasts
test_acc_3_train_cont_2 <- contrast(test_acc_3_train_means, 
                                  test_acc_3_train_coef_2, 
                                  by = "match_type", 
                                  adj = "hommel")

# Show
test_acc_3_train_cont_2
```

## Test 1: RT

### Filter, factor, and scale variables

```{r test_3_6}
# Filter and factor
dat_test_3_rt <- dat_test_rt %>%
  dplyr::filter(version %in% c("2a", "2b")) %>%
  mutate(across(.cols = c("participant", "prime", "target", "match_type"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_prime_cent = scale(FreqZipfUS_prime)[,1],
         freq_target_cent = scale(FreqZipfUS_target)[,1]) %>%
  left_join(tab_exp, by = "cond_exp")

# Add contrasts
contrasts(dat_test_3_rt$cond_exp_fac) <- contrast_train
contrasts(dat_test_3_rt$match_type) <- contrast_match_2
```

### Run model

```{r test_3_7, cache = TRUE}
# Run
test_rt_3_train <- lmer(inv_rt ~ cond_exp_fac*match_type + 
                          trial_cent + freq_prime_cent:freq_target_cent + 
                          vot_cent +
                          (1|prime:target) + (1|participant),
                        data = dat_test_3_rt)

# Show
summary(test_rt_3_train)
```

### Test effects

```{r test_3_8}
# Test effects
test_rt_3_train_comp <- Anova(test_rt_3_train, test = "Chi", type = "III")

# Show
test_rt_3_train_comp
```

### Get means: Exposure x Target type interaction

```{r test_3_9}
# Get means
test_rt_3_train_means <- emmeans(test_rt_3_train, ~ cond_exp_fac*match_type)

# Show
test_rt_3_train_means %>% apa_rt() %>% select(-report)
```

### Compare means: Exposure x Target type interaction

```{r test_3_10}
# Select contrasts for Test-only group
test_rt_3_train_coef <- emmeans:::pairwise.emmc(levels(test_rt_3_train_means)$cond_exp_fac)
test_rt_3_train_coef <- test_rt_3_train_coef[c(1:4)]

# Run contrasts
test_rt_3_train_cont <- contrast(test_rt_3_train_means, 
                                 test_rt_3_train_coef, 
                                 by = "match_type", 
                                 adj = "hommel")

# Show
test_rt_3_train_cont
```

## Test 2: RT

### Filter, factor, and scale variables

```{r test_3_11}
# Filter and factor
dat_test_3_rt_exp <- dat_test_rt %>%
  dplyr::filter(version == "2a") %>%
  mutate(across(.cols = c("participant", "prime", "target", "match_type",
                          "cond_sim", "cond_var"),
                as.factor),
         trial_cent = scale(trial)[,1],
         vot_cent = scale(vot)[,1],
         freq_prime_cent = scale(FreqZipfUS_prime)[,1],
         freq_target_cent = scale(FreqZipfUS_target)[,1])

# Add contrasts
contrasts(dat_test_3_rt_exp$cond_sim) <- contrast_sim
contrasts(dat_test_3_rt_exp$cond_var) <- contrast_var
contrasts(dat_test_3_rt_exp$match_type) <- contrast_match_2
```

### Run model

```{r test_3_12, cache = TRUE}
# Run
test_rt_3_exp <- lmer(inv_rt ~ cond_sim*cond_var*match_type + 
                     trial_cent + freq_prime_cent:freq_target_cent + 
                     vot_cent +
                     (1|prime:target) + (1|participant),
                   data = dat_test_3_rt_exp)

# Show
summary(test_rt_3_exp)
```

### Test effects

```{r test_3_13}
# Test effects
test_rt_3_comp_exp <- Anova(test_rt_3_exp, test = "Chi", type = "III")

# Show
test_rt_3_comp_exp
```

### Get means: Two-way interactions with Target type

```{r test_3_14}
# Get means
test_rt_3_means_exp_var_2 <- emmeans(test_rt_3_exp, ~ cond_var*match_type)

# Show
test_rt_3_means_exp_var_2 %>% apa_rt() %>% select(-report)

# Get means
test_rt_3_means_exp_sim_2 <- emmeans(test_rt_3_exp, ~ cond_sim*match_type)

# Show
test_rt_3_means_exp_sim_2 %>% apa_rt() %>% select(-report)
```

### Compare means: Two-way interactions with Target type

```{r test_3_15}
# Run contrasts
test_rt_3_cont_exp_var_2 <- pairs(test_rt_3_means_exp_var_2,
                             by = "match_type", 
                             adj = "hommel")

# Show
test_rt_3_cont_exp_var_2

# Run contrasts
test_rt_3_cont_exp_sim_2 <- pairs(test_rt_3_means_exp_sim_2, 
                             by = "match_type", 
                             adj = "hommel")

# Show
test_rt_3_cont_exp_sim_2
```

### Get means: Variability x Similarity x Target type interaction

```{r test_3_16}
# Get means
test_rt_3_means_exp_3 <- emmeans(test_rt_3_exp, ~ cond_var*cond_sim*match_type)

# Show
test_rt_3_means_exp_3 %>% apa_rt() %>% select(-report)
```

### Compare means: Variability x Similarity x Target type interaction

```{r test_3_17}
# Run contrasts in Variability
test_rt_3_cont_exp_var_3 <- pairs(test_rt_3_means_exp_3,
                                  by = c("match_type", "cond_var"), 
                                  adj = "hommel")

# Show
test_rt_3_cont_exp_var_3

# Run contrasts in Similarity
test_rt_3_cont_exp_sim_3 <- pairs(test_rt_3_means_exp_3,
                                  by = c("match_type", "cond_sim"), 
                                  adj = "hommel")

# Show
test_rt_3_cont_exp_sim_3
```

